---
title: "Social Networks and Social Resources"
author: "Kejing Li"
date: "11/11/2019"
output: 
  pdf_document:
    toc: true
    toc_depth: 3
subtitle: "US vs China"
---
# Introduction
A social network is a social structure made up of a set of social actors (such as individuals or organizations), sets of dyadic ties, and other social interactions between actors. Countless research shows that individual’s mental and physical wellbeing is largely dependent on a quality social networks back up with necessary social resources. This report aims at exploring the contributing factors and patterns of satisfactory level towards life by analyzing selected aspects of social networks and social networks in USA and China.

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
library(knitr)
library(haven)
theme_set(theme_minimal())
```

# Data
The database **International Social Survey Programme: Social Networks and Social Resources - ISSP 2017** is the source data for the report. This dataset is collected during 13.01.2017 and 07.03.2019

## ISSP
The International Social Survey Programme (ISSP) is a continuing annual program of cross-national survey collaboration, covering a wide range of topics important for social science research. Since 1985 the ISSP provides international data sets, enabling cross-cultural and cross-temporal research.

## Social Networks
‘Social Networks’ is one of the eleven ISSP topic modules. ISSP Social Networks modules essentially deal with issues, such as nature and contacts with family members and friends, participation in associations and groups, duties and rights in social networks and social trust. 

## Selection Method
- Probability Sample
- Probability Sample: Simple random
- Probability Sample: Systematic random
- Probability Sample: Stratified
- Probability Sample: Multistage

## Mode of Data Collection
- Face-to-face interview
- Self-administered questionnaire
- Telephone interview

## Variables Selected for the analysis purpose 
1. v22 Q7b Whom to ask for help: in household when ill?
1. v23 Q7c Whom to ask for help: in depression?
1. v24 Q7d Whom to ask for help: in giving advice about family problems?
1. v25 Q7e Whom to ask for help: in enjoying a pleasant social occasion with?
1. v58 Q30 Life in general: How satisfied on the whole?
1. HOMPOP How many persons in household
1. URBRURAL Place of living: urban – rural

```{r read data, cache = TRUE}
#import and tidy
data <- read_sav("data/ZA6980_v2-0-0.sav")
analysis_data <- data %>%
  select("c_alphan", v22:v25, v58, "HOMPOP", "URBRURAL") %>%
  filter(c_alphan %in% c("CN", "US"))
colnames(analysis_data) <- c("country", "ill", "depression", "family_problems", "social_occasion", "satisfactory", "homepop", "urban_rural")
```

# Social Network
## Whom to ask for help
To analyze the social network, four help-seeking scenarios are investigated. As people would more likely to turn to those they trust or feel comfortable with, these questions give implications on their perceived social relationships.   

### In household when ill
As shown in Figure 1, both Americans and the Chinese are more likely to ask help from close family members when they are ill, while a discernible variation happens on the friend scale. Americans tend to seek help friends as well.

```{r ill}
analysis_data %>%
  ggplot(aes(x = ill, y = ..density.., color = country)) +
  geom_freqpoly() +
  scale_x_continuous(
    breaks = 1:9,
    labels = c(
      "Close family member", "More distant family member", "Close friend",
      "Neighbour", "Someone I work with", "Someone else", "No one", "Can't choose", "No answer"
    )
  ) +
  scale_y_continuous(breaks = NULL) +
  coord_flip() +
  labs(
    title = "Figure 1.Whom to ask for help:\n in household when ill?",
    x = "Ask ... for help",
    y = "Number of respondents in proportion",
    color = "Country",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

### In depression

```{r depression}
analysis_data %>%
  ggplot(aes(x = depression, y = ..density.., color = country)) +
  geom_freqpoly() +
  scale_y_continuous(breaks = NULL) +
  scale_x_continuous(
    breaks = 1:9,
    labels = c(
      "Close family member", "More distant family member", "Close friend",
      "Neighbour", "Someone I work with", "Someone else", "No one", "Can't choose", "No answer"
    )
  ) +
  coord_flip() +
  labs(
    title = "Figure 2.Whom to ask for help:\n in depression?",
    x = "Ask ... for help",
    y = "Number of respondents in proportion",
    color = "Country",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

### In giving advice about family problems
With a Similar pattern occurring in the situation of depression (Figure 2) and meeting family problems (Figure 3), close friends accounted for a higher proportion than the first scenario.

```{r Family Pproblems}
analysis_data %>%
  ggplot(aes(x = family_problems, y = ..density.., color = country)) +
  geom_freqpoly() +
  scale_y_continuous(breaks = NULL) +
  scale_x_continuous(
    breaks = 1:9,
    labels = c(
      "Close family member", "More distant family member", "Close friend",
      "Neighbour", "Someone I work with", "Someone else", "No one", "Can't choose", "No answer"
    )
  ) +
  coord_flip() +
  labs(
    title = "Figure 3.Whom to ask for help: \n in giving advice about family problems?",
    x = "Ask ... for help",
    y = "Number of respondents in proportion",
    color = "Country",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

### In enjoying a pleasant social occasion with
In figure 4, it can be learned that in terms of recreation, Americans will consider family members and friends almost equally, and there is smaller difference between these two groups among Chinese as well. People get more diverse options in positive scenarios than negative ones.

```{r  social occasion}
analysis_data %>%
  ggplot(aes(x = social_occasion, y = ..density.., color = country)) +
  geom_freqpoly() +
  scale_y_continuous(breaks = NULL) +
  scale_x_continuous(
    breaks = 1:9,
    labels = c(
      "Close family member", "More distant family member", "Close friend",
      "Neighbour", "Someone I work with", "Someone else", "No one", "Can't choose", "No answer"
    )
  ) +
  coord_flip() +
  labs(
    title = "Figure 4.Whom to ask for help: \n in enjoying a social occasion with?",
    x = "Ask ... for help",
    y = "Number of respondents in proportion",
    color = "Country",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

## Home population
From the above analysis, it is quite evident that close family members are the core of the social networks whatever the country is, though the Chinese more rely on families than Americans. 

Since the family is an indispensable element of social networks, a question arises on the active individuals that exerting the influence(Table 1). Here, the satisfactory level is included to see whether the number of family members positively related to the life satisfaction level of an individual. 

```{r home population}
home_population <- 
  analysis_data %>%
  group_by(country) %>%
  summarize(mean(homepop)) 
kable(home_population, 
      col.names = c("Country", "Average home population"), 
      caption =  "Home population by country",
      format = "latex",
      digits = 2,
      align = "c")
```

### China
For China, life satisfactory doesn’t seem to have a relationship with the home population. In figure 5, for any given number of home population, the majority of people (the lightest block in each column fall into that chosen home population all feel fairly satisfied, uninfluenced by the value of the home population. 

```{r Satisfactory and home population(China)}
analysis_data %>%
  filter(country == "CN") %>%
  count(homepop,satisfactory) %>%
  ggplot(aes(homepop,satisfactory))+
  geom_tile(aes(fill = n))+
  scale_x_continuous(breaks = seq(1, 13, 1))+
  scale_y_continuous(
    breaks = 1:7,
    labels = c(
      "Completely Satisfied ", "", "",
      "Neither", "", "", "Completely dissatisfied")) +
  labs(
    title = "Figure 5.Satisfactory levels by home populations(China) ",
    x = "Home polulation",
    y = "Satidfactory Level",
    fill = "Number",
    caption = "Source: International Social Survey Programme (ISSP)"
  )

```

### USA 
For the USA, shown in figure 6 homes of two or four people are in general more satisfied than the others, with the majority feel very satisfied. 

```{r Satisfactory and home population(USA)}
analysis_data %>%
  filter(country == "US") %>%
  count(homepop,satisfactory) %>%
  ggplot(aes(homepop,satisfactory))+
  geom_tile(aes(fill = n))+
  scale_x_continuous(breaks = seq(1, 13, 1))+
  scale_y_continuous(
    breaks = 1:7,
    labels = c(
      "Completely Satisfied", "", "",
      "Neither", "", "", "Completely dissatisfied")) +
  labs(
    title = "Figure 6.Satisfactory levels by home populations(USA) ",
    x = "Home polulation",
    y = "Satidfactory Level",
    fill = "Number",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

# Social resources 
Regarding social resources, the place of living is employed as an indicator. In China, fairly Satisfied holds true regardless of the place of living. However, in the USA, satisfactory levels concentrate around very satisfied and fairly satisfied with small fluctuation among places. Further investigation is needed to determine whether the difference between the two countries is caused by different social resources. 

```{r urban_rural and satisfactory level}

urban_rural_labs <- c("Big city",
             "Suburbs or outskirts",
             "Town",
             "Village",
             "Farm")
names(urban_rural_labs) <- c(1:5)
 
                     
analysis_data %>%
  ggplot(aes(satisfactory,..prop..))+
  geom_bar()+
  scale_x_continuous(
    breaks = 1:7,
    labels = 7:1) +
  scale_y_continuous(labels = scales::percent_format(accuracy = 1))+
  facet_grid(urban_rural ~ country,  labeller = labeller(urban_rural= urban_rural_labs))+
  labs(
    title = "Figure 7. Satisfactory level by place of living ",
    x = "Satisfactory Level",
    y = "Number",
    caption = "Source: International Social Survey Programme (ISSP)"
  )
```

# Conclusions
- Chinese are more family-oriented than Americans in terms of social networks. 
- Family is the core of social networks. 
- The home population doesn’t have an influence on life satisfactory in China, while in the US, homes of 2 and 4 are more satisfied than the others. 
- In general, Americans are more satisfied towards their life than Chinese.

# Citation
ISSP Research Group (2019): International Social Survey Programme: Social Networks and Social Resources - ISSP 2017. GESIS Data Archive, Cologne. ZA6980 Data file Version 2.0.0, doi:10.4232/1.13322


